\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-24 trunk/concepts.tex
updates to arch and results mostly cosmetic

  \begin{figure} \centering
    \includegraphics[scale=0.4]{figs/europa-pr-1.pdf}
    \caption{\small Timelines representing initial state and goals for a Shopping Agent.}
    \label{fig:europapr1}
  \end{figure}

@@

\begin{figure} 
  \centering
  \includegraphics[scale=0.4]{figs/europa-pr-merge.pdf}
  \caption{\small State of timelines after satisfying a goal to be
    home by time $20$ on merging with initial state.}
  \label{fig:europapr:merge}
\end{figure}

@@

\begin{figure} \centering
  \includegraphics[scale=0.4]{figs/europa-pr-activate.pdf}
  \caption{\small State of timelines after satisfying a goal to own a
    drill by time $10$ by activating corresponding token.}
\label{fig:europapr:activate}
\end{figure}

>>>>

  \begin{figure}[t]
    \centering \subfloat[\small Timelines representing initial state
    and goals for a Shopping
    Agent.]{\label{fig:europapr1}\includegraphics[scale=0.35]{figs/europa-pr-1.pdf}}\qquad
    \subfloat[\small State of timelines after satisfying a goal to be
    home by time $20$ on merging with initial
    state.]{\label{fig:europapr:merge}\includegraphics[scale=0.35]{figs/europa-pr-merge.pdf}}\qquad
    \subfloat[\small State of timelines after satisfying a goal to own
    a drill by time $10$ by activating corresponding
    token.]{\label{fig:europapr:activate}\includegraphics[scale=0.35]{figs/europa-pr-activate.pdf}}
    \caption{\small Evolution of a timeline from the Shopping Agent example}
  \end{figure}

@@

% \begin{figure} 
%   \centering
%   \includegraphics[scale=0.4]{figs/europa-pr-merge.pdf}
%   \caption{\small State of timelines after satisfying a goal to be
%     home by time $20$ on merging with initial state.}
%   \label{fig:europapr:merge}
% \end{figure}

@@

% \begin{figure} \centering
%   \includegraphics[scale=0.4]{figs/europa-pr-activate.pdf}
%   \caption{\small State of timelines after satisfying a goal to own a
%     drill by time $10$ by activating corresponding token.}
% \label{fig:europapr:activate}
% \end{figure}

### 2012-02-24 trunk/europa.tex
updates to arch and results mostly cosmetic

\item[\textbf{Object Types}]: \texttt{NDDL} supports an object-oriented
  approach, where common data and behavior can be abstracted as a
  class. In this case, we have the \textit{Product} class represent
  the products that the Shopping Agent needs, \textit{Location}
  represents the places where products can be found,
  \textit{ProductLocation} represents the association arising when a
  product can be purchased at a location. The Shopping Agent itself is
  represented by an \textit{Agent} class, which relies on the
  \textit{AgentLocation} class to keep track of where the agent is at
  any point in time. \texttt{NDDL} supports a single rooted class
  hierarchy so that state and behavior can be extended through
  inheritance. We take advantage of that feature by making
  \textit{AgentLocation} inherit from \eus built-in \textit{Timeline}
  class which doesn't allow predicates to overlap in time for the same
  object instance. This feature is used for instance, to ensure that
  an agent can only be at one place at a time in our example.

\item[\textbf{Variable Types and Instances}]: All object attributes
  are represented as variables in this model. For instance, it uses
  integer variables to represent the built-in temporal parameters for
  each token (activity duration, start and end times), string
  variables to represent \textit{Location} and \textit{Product} names,
  and object reference variables to represent the structural
  relationships between different objects (for instance, each Agent
  maintains a variable to keep track of its \textit{AgentLocation}).

\item[\textbf{Predicate Types}]: Some classes like \textit{Product},
  \textit{Location} and \textit{ProductLocation} are static and so
  don't have any predicate or action types associated with them. The
  \textit{AgentLocation} class is used to keep track of state and so
  has \texttt{At} and \texttt{Going} predicate types associated with
  it. The \textit{Agent} class keeps track of the products it
  purchases through the \texttt{Own} predicate; having a separate
  \textit{AgentBag} class with its own predicates would have been an
  equally valid modeling choice.

\item[\textbf{Action Types}]: In our example, \textit{Agent} is solely
  the class that has behavior associated with it. Consequently, it
  defines action types to represent when the agent is taking action to
  \texttt{Go} to a \textit{Location}, or to \texttt{Buy} a
  \textit{Product}. % We'll see how the actual behavior for those
  % actions is specified below.

@@

\item[\textbf{Variables}]: A token type (predicate or action) is part
  of a class, therefore class attributes (see \texttt{object.location}
  above), token type parameters (see \texttt{[from, to]} in
  \texttt{Agent::Go}, or \texttt{[duration, product]} in
  \texttt{Agent::Buy}) and locally declared variables (see
  \texttt{possibleStores} in \texttt{Agent::Buy}) can all be used in
  the definition of a rule.

\item[\textbf{Constraints}]: Restrictions on values that variables can
  take within a rule are expressed through constraints. In the example
  above the \texttt{eq} constraint is used; in general, any constraint
  available in \eus library can be used.

\item[\textbf{Subgoals}]: In \texttt{Agent::Go}, subgoals are used to
  specify that the Shopping Agent's location must transition from
  origin to destination in a temporally consistent way. The
  \texttt{[meets, equals, metby]} operators (see Section
  \ref{sec:europa:inference}) are used to specify subgoals, along with
  the temporal relationship each token representing a subgoal has with
  the the token representing the \texttt{Agent::Go} action. Also,
  \texttt{[condition, effect]} annotations can be used when defining a
  subgoal inside an action. Currently \eu does not associate semantics
  with these annotation; but they can be extremely useful for search
  modules when creating plans.

@@

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.3]{figs/Allen-algebra.pdf}
\caption{\small Temporal relations defined within the planner are
  based on \texttt{Allen Algebra} relations shown above.}
\label{fig:allen-algebra}
\end{figure}

In \eu, problem domains use \texttt{Allen Algebra} \cite{allen84}
temporal relations shown in Fig. \ref{fig:allen-algebra} which allow
encoding of temporal constraint relationships between tokens on
concurrent timelines. \kcomment{This para could do with a little
  embellishment especially since it is the only material that actually
  talks about the kinds of constraints and their origin.}

@@

In \eue, all variables and constraints from a problem domain
description are stored inside the \texttt{CRE}.  The \texttt{CRE}
provides a framework where any number of constraint types can
collaborate to perform inference and prune variable domains using
Bounds Propagation and Domain Reduction techniques \kcomment{citation
  needed}. \eu uses a Propagator pattern which keeps track of a set of
constraint instances of the same type and is responsible for ensuring
variables are inferentially updated with change (modifications or
constraint addition/deletion).

@@

\item[\textbf{Unbound Variable}]: a variable in the partial plan whose
  domain is not a singleton. Unbound Variables are resolved by value
  selection from their domain.

\item[\textbf{Open Condition}]: an open condition is an
  \texttt{INACTIVE} token. \texttt{INACTIVE} tokens can be generated
  by explicitly posted goals, or when a token is activated, rules may
  activate the creation of \texttt{INACTIVE} slave tokens as described
  in Section \ref{sec:europa:pr}. Open Conditions can be resolved in
  three ways:

@@

  \item[\textbf{Merging}]: A free activity is merged with a matching
    activity already in the plan. An activity $a$ is said to match an
    activity $a?$ iff $a$ and $a?$ unify \cite{russelnorvig} and the
    temporal constraints involving $a$ are satisfied by $a?$. Thus,
    $a$ and $a?$ can be considered the same activity without the need
    to introduce $a$ in the plan. Consequently, the compatibilities
    \kcomment{compatibilities have not been defined} associated with
    $a$ are not Þred \kcomment{???}, because they have been already
    triggered when $a?$ was introduced in the plan.

  \item[\textbf{Activation}]: A new activity $a$ is introduced in the
    current plan associating it with the correct timeline, without
    choosing a specific time slot. The compatibilities \kcomment{as
      above} associated with $a$ are applied and the subgoal
    activities resulting from those compatibilities \kcomment{as
      above} are introduced as free activities \kcomment{what is a
      free activity?}. This results in both an ordering flaw
    \kcomment{undefined}, corresponding to the just activated
    activity, and a number of open condition flaws, corresponding to
    the new subgoal activities.

  \item[\textbf{Rejection}]: Some goals may be optional; if so its
    corresponding flaw can be resolved by discarding the
    \texttt{INACTIVE} token.

@@

\item[\textbf{Threat}]: Once a token has been placed in the partial
  plan it may impact other tokens indirectly through possible
  overlapping requirements on objects. Recall for example that a token
  may belong to objects (\eg timelines) which require a total order
  over their tokens. If any two tokens could possibly overlap (though
  not necessarily), then they pose a threat to each other in terms of
  achieving an extension of the current partial plan which is complete
  and consistent. Similarly, threats may arise where tokens share a
  common resource and their current state might yield extensions of
  the current partial plan which are inconsistent. Threats are
  resolved by imposing ordering constraints among tokens.

@@

\item[Line \textbf{\ref{li:propagate}}]: Propagate the constraints to
  test for inconsistency. If inconsistent, then return false since no
  refinements to $p$ can yield a consistent plan.

\item[Line \textbf{\ref{li:selectflaw}}]: Choose a flaw from the set
  of available flaws.

\item[Line \textbf{\ref{li:noflaw}}]: If there are no flaws, then $p$
  is complete and terminate with success.

\item[Line \textbf{\ref{li:decisionpt}}]: Formulate a decision point
  which is a branch in the search space. Each choice is a particular
  refinement operation and the \texttt{DecisionPoint} collects all
  possible refinement operations for the given flaw.

\item[Line \textbf{\ref{li:decisionloop}}]: Keep trying until the
  chosen flaw is resolved, or until there are no further resolvers to
  try.

\item[Line \textbf{\ref{li:decide}}]: A new partial plan is obtained
  by application of a refinement operator. Note that the ordering over
  refinement operators to select is a non-deterministic step.

\item[Line \textbf{\ref{li:recurse}}]: Recursive call to solve the
  new planning problem. If successful, then success.

\item[Line \textbf{\ref{li:backtrack}}]: Otherwise, retract the last
  refinement operation and move on to try the next one.

\item[Line \textbf{\ref{li:noplan}}]: Arriving here implies all
  options to resolve the flaw have been exhausted, including the case
  where no options were available initially. Thus the problem is
  insoluble.

>>>>

\item[\textbf{Object Types}:] \texttt{NDDL} supports an object-oriented
  approach, where common data and behavior can be abstracted as a
  class. In this case, we have the \textit{Product} class represent
  the products that the Shopping Agent needs, \textit{Location}
  represents the places where products can be found,
  \textit{ProductLocation} represents the association arising when a
  product can be purchased at a location. The Shopping Agent itself is
  represented by an \textit{Agent} class, which relies on the
  \textit{AgentLocation} class to keep track of where the agent is at
  any point in time. \texttt{NDDL} supports a single rooted class
  hierarchy so that state and behavior can be extended through
  inheritance. We take advantage of that feature by making
  \textit{AgentLocation} inherit from \eus built-in \textit{Timeline}
  class which doesn't allow predicates to overlap in time for the same
  object instance. This feature is used for instance, to ensure that
  an agent can only be at one place at a time in our example.

\item[\textbf{Variable Types and Instances}:] All object attributes
  are represented as variables in this model. For instance, it uses
  integer variables to represent the built-in temporal parameters for
  each token (activity duration, start and end times), string
  variables to represent \textit{Location} and \textit{Product} names,
  and object reference variables to represent the structural
  relationships between different objects (for instance, each Agent
  maintains a variable to keep track of its \textit{AgentLocation}).

\item[\textbf{Predicate Types}:] Some classes like \textit{Product},
  \textit{Location} and \textit{ProductLocation} are static and so
  don't have any predicate or action types associated with them. The
  \textit{AgentLocation} class is used to keep track of state and so
  has \texttt{At} and \texttt{Going} predicate types associated with
  it. The \textit{Agent} class keeps track of the products it
  purchases through the \texttt{Own} predicate; having a separate
  \textit{AgentBag} class with its own predicates would have been an
  equally valid modeling choice.

\item[\textbf{Action Types}:] In our example, \textit{Agent} is solely
  the class that has behavior associated with it. Consequently, it
  defines action types to represent when the agent is taking action to
  \texttt{Go} to a \textit{Location}, or to \texttt{Buy} a
  \textit{Product}. % We'll see how the actual behavior for those
  % actions is specified below.

@@

\item[\textbf{Variables}:] A token type (predicate or action) is part
  of a class, therefore class attributes (see \texttt{object.location}
  above), token type parameters (see \texttt{[from, to]} in
  \texttt{Agent::Go}, or \texttt{[duration, product]} in
  \texttt{Agent::Buy}) and locally declared variables (see
  \texttt{possibleStores} in \texttt{Agent::Buy}) can all be used in
  the definition of a rule.

\item[\textbf{Constraints}:] Restrictions on values that variables can
  take within a rule are expressed through constraints. In the example
  above the \texttt{eq} constraint is used; in general, any constraint
  available in \eus library can be used.

\item[\textbf{Subgoals}:] In \texttt{Agent::Go}, subgoals are used to
  specify that the Shopping Agent's location must transition from
  origin to destination in a temporally consistent way. The
  \texttt{[meets, equals, metby]} operators (see Section
  \ref{sec:europa:inference}) are used to specify subgoals, along with
  the temporal relationship each token representing a subgoal has with
  the the token representing the \texttt{Agent::Go} action. Also,
  \texttt{[condition, effect]} annotations can be used when defining a
  subgoal inside an action. Currently \eu does not associate semantics
  with these annotation; but they can be extremely useful for search
  modules when creating plans.

@@

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.3]{figs/Allen-algebra.pdf}
\caption{\small Temporal relations defined within the planner are
  based on \texttt{Allen Algebra} \cite{allen84} relations shown
  above.}
\label{fig:allen-algebra}
\end{figure}

In \eu, problem domains use \texttt{Allen Algebra} \cite{allen84}
temporal relations shown in Fig. \ref{fig:allen-algebra} which allow
encoding of temporal constraint relationships between tokens.
\kcomment{This para could do with a little embellishment especially
  since it is the only material that actually talks about the kinds of
  constraints and their origin.JB: I don't really know what else to
  say given the table above.}

@@

In \eue, all variables and constraints from a problem domain
description are stored inside the \texttt{CRE}.  The \texttt{CRE}
provides a framework where any number of constraint types can
collaborate to perform inference and prune variable domains using
Bounds Propagation and Domain Reduction techniques \cite{marriott98}. 
\eu uses a Propagator pattern which keeps track of a set of
constraint instances of the same type and is responsible for ensuring
variables are inferentially updated upon change (domain modifications or
constraint addition/deletion).

@@

\item[\textbf{Unbound Variable}:] a variable in the partial plan whose
  domain is not a singleton. Unbound Variables are resolved by value
  selection from their domain.

\item[\textbf{Open Condition}:] an open condition is an
  \texttt{INACTIVE} token. \texttt{INACTIVE} tokens can be generated
  by explicitly posted goals, or when a token is activated, rules may
  activate the creation of \texttt{INACTIVE} slave tokens as described
  in Section \ref{sec:europa:pr}. Open Conditions can be resolved in
  three ways:

@@

  \item[\textbf{Merging}:] A free activity \kcomment{this could be
      defined, since no def. for 'free' is provided} is merged with a
    matching activity already in the plan. An activity $a$ is said to
    match an activity $a?$ iff $a$ and $a?$ unify \cite{russelnorvig}
    and the temporal constraints involving $a$ are satisfied by
    $a?$. Thus, $a$ and $a?$ can be considered the same activity
    without the need to introduce $a$ in the plan. Consequently, the
    domain rules associated with $a$ are not introduced into the
    planning process, since they are already triggered when $a?$ was
    introduced in the plan.

  \item[\textbf{Activation}:] A new activity $a$ is introduced in the
    current plan associating it with the appropriate timeline, without
    choosing a specific time slot; if its timing causes a problem a
    Threat flaw will be triggered (see below).  The domain rules
    associated with $a$ are applied and the subgoal activities
    resulting from those domain rules are introduced as inactive
    tokens.  This results in a number of open condition flaws,
    corresponding to the new subgoal activities.

  \item[\textbf{Rejection}:] Some goals may be optional; if so its
    corresponding flaw may be resolved by discarding the
    \texttt{INACTIVE} token.

@@

\item[\textbf{Threat}:] Once a token has been placed in the partial
  plan it may impact other tokens indirectly through possible
  overlapping requirements on objects. Recall for example that a token
  may belong to objects (\eg timelines) which require a total order
  over their tokens. If any two tokens could possibly overlap (though
  not necessarily), then they pose a threat to each other in terms of
  achieving an extension of the current partial plan which is complete
  and consistent. Similarly, threats may arise where tokens share a
  common resource and their current state might yield extensions of
  the current partial plan which are inconsistent. Threats are
  resolved by imposing ordering constraints among tokens.

@@

\item[Line \textbf{\ref{li:propagate}}:] Propagate the constraints to
  test for inconsistency. If inconsistent, then return false since no
  refinements to $p$ can yield a consistent plan.

\item[Line \textbf{\ref{li:selectflaw}}:] Choose a flaw from the set
  of available flaws.

\item[Line \textbf{\ref{li:noflaw}}:] If there are no flaws, then $p$
  is complete and terminate with success.

\item[Line \textbf{\ref{li:decisionpt}}:] Formulate a decision point
  which is a branch in the search space. Each choice is a particular
  refinement operation and the \texttt{DecisionPoint} collects all
  possible refinement operations for the given flaw.

\item[Line \textbf{\ref{li:decisionloop}}:] Keep trying until the
  chosen flaw is resolved, or until there are no further resolvers to
  try.

\item[Line \textbf{\ref{li:decide}}:] A new partial plan is obtained
  by application of a refinement operator. Note that the ordering over
  refinement operators to select is a non-deterministic step.

\item[Line \textbf{\ref{li:recurse}}:] Recursive call to solve the
  new planning problem. If successful, then success.

\item[Line \textbf{\ref{li:backtrack}}:] Otherwise, retract the last
  refinement operation and move on to try the next one.

\item[Line \textbf{\ref{li:noplan}}:] Arriving here implies all
  options to resolve the flaw have been exhausted, including the case
  where no options were available initially. Thus the problem is
  insoluble.

### 2012-02-24 trunk/results.tex
updates to arch and results mostly cosmetic

\begin{figure}[htpb]
\centering
\includegraphics[scale=0.65]{figs/inl.jpg}
\caption{\small An Intermediate Nepheloid Layer (INL) detected by an
  AUV mission in the Monterey Bay in August 2005, showing the location
  of the AUV transect in the bay (left) and optical backscatter image
  at the 420 Nm frequency showing the INLs patchy nature
  (right). \emph{Image courtesy: John Ryan, MBARI}}
\label{fig:inl}
\end{figure}

@@

\begin{figure}[htpb]
\centering
\includegraphics[width=0.8\textwidth]{figs/front-mi.jpg}
\caption{\small{Survey trackline of AUV following a thermal
    gradient. Image in the middle shows the temperature while the
    bottom figure shows different phases in the algorithm.}}
\label{fig:mi-front}
\end{figure}

@@

\begin{figure}[htpb]
\centering
\includegraphics[width=0.5\textwidth]{figs/dta-app.pdf}
\caption{\small{Overall setup of \can lagrangian experiments with a
    drifting instrument pack. Various combinations of computational
    methods can be included in the Drifter Tracking App which is a
    part of the Oceanographic Decision Support System (\od)
    \cite{das11}.}}
\label{fig:dta-setup}
\end{figure}

@@

\begin{figure}[htpb]
\centering
\includegraphics[width=0.7\textwidth]{figs/oct10-ballet.pdf}
\caption{\small An October 2010 robot ``ballet'' where a smaller
  slower AUV tracked a patch center, sending periodic updates to the
  Dorado using a setup shown in Fig. \ref{fig:dta-setup}. The Google
  Earth post-hoc image shows {\color{red}red} track lines of the \rx
  commanded Dorado with the {\color{yellow}yellow} transects of the
  LRAUV. {\color{yellow}Yellow} dots show the track line of a
  GPS-enabled drifter used for seeding the experiment over the
  Monterey Canyon with Santa Cruz, California to the right of the
  figure.}
\label{fig:ballet}
\end{figure}

@@

\begin{figure*}
  \centering
  \subfloat[A conceptual view of the \od]{\label{fig:odss-concept}\includegraphics[width=0.5\textwidth]{figs/odss-concept.pdf}}\\
  \subfloat[Current Implementation for
  \can]{\label{fig:odss-frontend}\includegraphics[width=0.5\textwidth]{figs/dss-screenshot.png}}
\caption{\small The Oceanographic Decision Support System (\od) is a
  single portal for planning, visualization, situational awareness,
  collaboration and archival of information before, during and after
  field experiments. The \od has been used since mid-year 2010 for
  \can field experiments.}
\label{fig:odss}
\end{figure*}

@@

\begin{figure*}
\centering
\subfloat[]{\label{fig:odss-mtg}\includegraphics[width=0.3\textwidth]{figs/october-canon-meeting.png}}
\subfloat[]{\label{fig:odss-virtual}\includegraphics[width=0.33\textwidth]{figs/virtual-drifter-tool.png}}
\subfloat[]{\label{fig:odss-ipad}\includegraphics[width=0.3\textwidth]{figs/photo-ipad-2.jpg}}
\caption{\small \ref{fig:odss-mtg} shows a 2010 \can meeting with the
  \od in use. \ref{fig:odss-virtual} shows a drifter tracking tool
  used during \can planning; it used a physical model of advected
  surface currents from \texttt{CeNCOOS} \cite{cencoos} to plan AUV
  deployments. \ref{fig:odss-ipad} shows \od use on a portable iPad
  device.}
\label{fig:odss2}
\end{figure*}

>>>>

\begin{figure}[b]
\centering
\includegraphics[scale=0.65]{figs/inl.jpg}
\caption{\small An Intermediate Nepheloid Layer (INL) detected by an
  AUV mission in the Monterey Bay in August 2005, showing the location
  of the AUV transect in the bay (left) and optical backscatter image
  at the 420 Nm frequency showing the INLs patchy nature
  (right). \emph{Image courtesy: John Ryan, MBARI}}
\label{fig:inl}
\end{figure}

@@

\begin{figure}[b]
\centering
\includegraphics[width=0.8\textwidth]{figs/front-mi.jpg}
\caption{\small{Survey trackline of AUV following a thermal
    gradient. Image in the middle shows the temperature while the
    bottom figure shows different phases in the algorithm.}}
\label{fig:mi-front}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.5\textwidth]{figs/dta-app.pdf}
\caption{\small{Overall setup of \can lagrangian experiments with a
    drifting instrument pack. Various combinations of computational
    methods can be included in the Drifter Tracking App which is a
    part of the Oceanographic Decision Support System (\od)
    \cite{das11}.}}
\label{fig:dta-setup}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.7\textwidth]{figs/oct10-ballet.pdf}
\caption{\small An October 2010 robot ``ballet'' where a smaller
  slower AUV tracked a patch center, sending periodic updates to the
  Dorado using a setup shown in Fig. \ref{fig:dta-setup}. The Google
  Earth post-hoc image shows {\color{red}red} track lines of the \rx
  commanded Dorado with the {\color{yellow}yellow} transects of the
  LRAUV. {\color{yellow}Yellow} dots show the track line of a
  GPS-enabled drifter used for seeding the experiment over the
  Monterey Canyon with Santa Cruz, California to the right of the
  figure.}
\label{fig:ballet}
\end{figure}

@@

\begin{figure*}
  \centering
  \subfloat[A conceptual view of the \od and how it fits into \can
  field experiments]{\label{fig:odss-concept}\includegraphics[width=0.5\textwidth]{figs/odss-concept.pdf}}\\
  \subfloat[Current implementation of \od for
  \can]{\label{fig:odss-frontend}\includegraphics[width=0.5\textwidth]{figs/dss-screenshot.png}}
\caption{\small The Oceanographic Decision Support System (\od) is a
  single portal for planning, visualization, situational awareness,
  collaboration and archival of information before, during and after
  field experiments. The \od has been used since mid-year 2010 for
  \can field experiments.}
\label{fig:odss}
\end{figure*}

@@

\begin{figure*}
\centering
\subfloat[]{\label{fig:odss-mtg}\includegraphics[width=0.3\textwidth]{figs/october-canon-meeting.png}}
\subfloat[]{\label{fig:odss-virtual}\includegraphics[width=0.33\textwidth]{figs/virtual-drifter-tool.png}}
\subfloat[]{\label{fig:odss-ipad}\includegraphics[width=0.3\textwidth]{figs/photo-ipad-2.jpg}}
\caption{\small \ref{fig:odss-mtg} shows a 2010 \can meeting with the
  \od in use. \ref{fig:odss-virtual} shows a drifter tracking tool
  used during \can planning; it used a physical model of advected
  surface currents from \texttt{CeNCOOS} \cite{cencoos} to plan AUV
  deployments. \ref{fig:odss-ipad} shows \od use on an iPad.}
\label{fig:odss2}
\end{figure*}
